Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2016-11-01 paper.tex
Add relation between emissivities eta and j

\subsection{Absorption and emission via charged current}
\label{ssec:sources_ae}
At neutrino and thermal energies well below $m_{\mu}\sim100\,{\rm MeV}$
only charged current processes involving $\nu_e$ and $\bar{\nu}_e$ are allowed.
For each of these processes, $i$, we may write an emission and absorption
coefficient as a function of the interaction cross-section
(e.g. \cite[Eqn.~A5]{brue1985-core_collapse}):
\todo{explain Fermi-blocking}
\begin{align}
  \label{eqn:sources_ae_1}
  C_{{\rm AE},i}
  &= \mathscr{E}_{{\rm AE},i} (1-f) - \mathscr{K}_{{\rm AE},i} f \\
  \label{eqn:sources_ae_2}
  &= \mathscr{E}_{{\rm AE},i} - (\mathscr{E}_{{\rm AE},i} + \mathscr{K}_{{\rm AE},i}) f,
\end{align}
with
\begin{equation}
  \label{eqn:inv_emissivity}
  \mathscr{E}_{{\rm AE},i} = \frac{(2\pi)^3}{\varepsilon^2}\eta_{i},
\end{equation}
where $\eta$ is the traditional emissivity with dimension
$[\eta]={\rm energy}\,{\rm length}^{-3}\,{\rm time}^{-1}\,{\rm energy}^{-1}\,{\rm steradian}^{-1}$,
and
\begin{equation}
  \label{eqn:inv_opacity}
  \mathscr{K}_{{\rm AE},i} = \varepsilon \chi_i,
\end{equation}
where $\chi$ is the traditional opacity with dimension
$[\chi]={\rm length}^{-1}$.

>>>>

\subsection{Absorption and emission via charged current}
\label{ssec:sources_ae}
At neutrino and thermal energies well below $m_{\mu}\sim100\,{\rm MeV}$
only charged current processes involving $\nu_e$ and $\bar{\nu}_e$ are allowed.
For each of these processes, $i$, we may write an emission and absorption
coefficient as a function of the interaction cross-section
(e.g. \cite[Eqn.~A5]{brue1985-core_collapse}):
\todo{explain Fermi-blocking}
\begin{align}
  \label{eqn:sources_ae_1}
  C_{{\rm AE},i}
  &= \mathscr{E}_{{\rm AE},i} (1-f) - \mathscr{K}_{{\rm AE},i} f \\
  \label{eqn:sources_ae_2}
  &= \mathscr{E}_{{\rm AE},i} - (\mathscr{E}_{{\rm AE},i} + \mathscr{K}_{{\rm AE},i}) f,
\end{align}
with
\begin{equation}
  \label{eqn:inv_emissivity}
  \mathscr{E}_{{\rm AE},i}
  = \varepsilon j_i
  = \frac{(2\pi)^3}{\varepsilon^2}\eta_i,
\end{equation}
where $j$ is the emissivity having dimension
$[j]={\rm length}^{-1}\,{\rm steradian}^{-1}$,
$\eta$ is the emissivity having dimension
$[\eta]={\rm energy}\,{\rm length}^{-3}\,{\rm time}^{-1}\,{\rm energy}^{-1}\,{\rm steradian}^{-1}$
(natural to formulations using specific intensity instead of distribution
functions), and
\begin{equation}
  \label{eqn:inv_opacity}
  \mathscr{K}_{{\rm AE},i} = \varepsilon \chi_i,
\end{equation}
where $\chi$ is the traditional opacity with dimension
$[\chi]={\rm length}^{-1}$.
